---
title: "Data Analysis Project - Understanding Human's Motor system"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library('tidyverse')
library('dplyr')
library('expss')
library('compare')
library('rstatix')
library('ggpubr')
library('janitor')
library('wesanderson')
library('ggplot2')
knitr::opts_chunk$set(echo = TRUE)

exp1 <- read_csv('exp1.csv')
```

## **Background**

In this project we're going to use visualization, T-test and linear regression in order to explore:

1. is action-effect improves accuracy?  

2. The relationship between ttime to accuracy
```
**Raw data**
```{r Raw, exercise=TRUE}

head(exp1)

```

**Data Preparation**

```{r Datapreparation, exercise=TRUE}
exp1_p = exp1 %>% rename( breaks= "break", subnum = participantid)
exp1_p$block_condition = exp1_p$target

#Remove outliers and creating new variables
exp1_p  = exp1_p %>%
  filter(interruptions==2 & device<=2 & controller == 1)%>%
  mutate(x1 = ((x /cm)*10))%>%
  mutate(y1 = (y /cm)*10) %>%
  mutate(xy = (x1*x1)+(y1*y1)) %>%
  mutate(distance = (xy^0.5))

p_suc<-exp1_p %>% 
  group_by(subnum)
  
p_success<- p_suc%>%summarize(total = n(),correct = sum(success))%>%mutate(pcorrect = correct/total)%>%select(subnum,pcorrect)

exp1_p_1 <-exp1_p %>% left_join(p_success)



###calculating flash impact
exp1_p_ar<-exp1_p_1%>%arrange(subnum,block_condition,trial)%>%select(subnum,block_condition,trial,distance,ftime,ttime,success,pcorrect,lag,aq_score)
exp1_p_ar["distance1"]<- 0.05
exp1_p_ar["ftime1"]<- 0.05
exp1_p_ar["ttime1"]<- 0.05
exp1_p_ar["success1"]<- 0.05
exp1_p_ar["pcorrect1"]<- 0.05



for (j in 1:(nrow(exp1_p_ar)-1))
{
  if ((exp1_p_ar[j,1]==exp1_p_ar[j+1,1])&(exp1_p_ar[j,2]==exp1_p_ar[j+1,2]))
  {  
    
    exp1_p_ar[j,11]<-exp1_p_ar[j+1,4]
    exp1_p_ar[j,12]<-exp1_p_ar[j+1,5]
    exp1_p_ar[j,13]<-exp1_p_ar[j+1,6]
    exp1_p_ar[j,14]<-exp1_p_ar[j+1,7]
    exp1_p_ar[j,15]<-exp1_p_ar[j+1,8]
  }
  else
  {
    
    exp1_p_ar[j,11]<-0.05
    exp1_p_ar[j,12]<-0.05
    exp1_p_ar[j,13]<-0.05
    exp1_p_ar[j,14]<-0.05
    exp1_p_ar[j,15]<-0.05
  }
}

###Cleaning outliers and unnecessary observations for t-test
exp1_p_ar = exp1_p_ar %>% filter(pcorrect1>=0.85) %>% filter(success1 !=0 & success !=0)%>%filter(ttime<=3000 & ttime1<=3000)%>%filter(lag==300)

###Preparing data for T-test by calculating for each block condition
exp1_ready =exp1_p_ar%>% group_by(subnum,block_condition)%>%summarize(mean_distance1 = mean(distance1),sd_distance1 = sd(distance1),mean_ttime1 = mean(ttime1),mean_ftime1 = mean(ftime1),aq_score = mean(aq_score))
exp1_t_test = exp1_ready%>% arrange(block_condition,subnum)


###Preparing data for Linear Regression
ready_for_reg = exp1_ready %>%
  group_by(subnum) %>%
  mutate(Diff_distance = (mean_distance1) - lag((mean_distance1)),Diff_time = (mean_ttime1) - lag((mean_ttime1)))%>%drop_na()%>%select(subnum,Diff_distance,Diff_time)
```

**T-Test**
```{r T_test, exercise=TRUE}
p1 = ggplot(exp1_t_test, aes(x=block_condition, y=mean_distance1,fill = block_condition))
stat.test = t.test(mean_distance1 ~ block_condition,data = exp1_t_test, paired = TRUE, mu = 0)
stat.test

```


**Plotting T-Test**
```{r Box_gitter plot  , exercise=TRUE}


p1+geom_boxplot()+
geom_jitter(width=0.25, alpha=0.8)
```


```{r violin_gitter plot  , exercise=TRUE}
p1+
  geom_violin(trim=FALSE)+
  geom_jitter(width=0.25, alpha=0.8)+
  scale_fill_manual(values = wes_palette("Darjeeling2", n = 2))
```

```{r violin_box plot  , exercise=TRUE}

p1 +
  geom_violin(trim=FALSE, alpha=0.7)+
  geom_boxplot(width=0.3)+
  scale_fill_manual(values = wes_palette("Darjeeling2", n = 2))

```

**Linear Regression Model**

```{r Linear Regression, exercise=TRUE}

model <- lm(Diff_time ~ Diff_distance, data = ready_for_reg)
summary(model)
```

**Scatter Plot**

```{r Scatter_Linear  , exercise=TRUE}

ggplot(ready_for_reg, aes(Diff_time, Diff_distance)) +
geom_point() +
geom_smooth(method = lm,se = FALSE)
```
